---
title: "tidyverse_assignment"
author: "Charls Joseph"
date: "December 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tidyverse assignment. 


in this assignment, I was asked to explore a tidyverse package and show an example on how it works. 
Here, I am trying to explore 'purrr' and broom packages and see what features it provides. 

## purrr and broom packages 

`purrr` is kind of like `dplyr` for lists. It helps you repeatedly apply functions.  `purrr` makes the API consistent, encourages type specificity, and provides some nice shortcuts and speed ups. Lets explore some basic usage and dive into some complex use-cases.  



```{r}
library(purrr)
library(dplyr)

map(1:4,  sqrt)

# using a formulae with tilde 
map(1:4,  ~ sqrt(2*.))
map(1:4,  ~ log(3, base = .))

```

# map_xxx  type-specifies the output type. 

```{r}
map_dbl(1:4,  ~ log(3, base = .))
#And throws an error if any output isn't of the expected type (which is a good thing!).

```


`map2` is like `mapply` -- apply a function over two lists in parallel. `map_n` generalizes to any number of lists.

```{r map2}
fwd = 1:10
bck = 10:1
map2_dbl(fwd, bck, `^`)
```


`map_if` tests each element on a function and if true applies the second function, if false returns the original element.

```{r map_if}
data_frame(ints = 1:5, lets = letters[1:5], sqrts = ints^.5) %>% map_if(is.numeric, ~ .^2) 
```

Let's see if we can really make this purrr... Fit a linear model of winpercent by every combination of two predictors in the dataset and see which two predict best. We will select predictors who 'rmse' ( root mean square error) is lesser.  

```{r}
library(readr)
candy_data <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/candy-power-ranking/candy-data.csv")

test <- candy_data[1:19 , ]
head(candy_data)

```

'augment' is a method from broom package that returns information about individual observations to a dataset, such as fitted values or influence measures.

```{r diamonds predictors}

library(broom)
train = sample(nrow(candy_data), floor(nrow(candy_data) * .67))

testdata <- candy_data[1:56 , ]
head(testdata)

setdiff(names(candy_data), "winpercent") %>%
  combn(2, paste, collapse = " + ") %>%
  structure(., names = .) %>%
  map(~ formula(paste("winpercent ~ ", .x))) %>%
  map(lm, data = candy_data[train, ]) %>%
  map_df(augment, newdata = testdata, .id = "predictors") %>%
  group_by(predictors) %>% summarize(rmse = sqrt(mean((winpercent - .fitted)^2))) %>%
  arrange(rmse)
```


